---
title: "Untitled"
author: "ziyu"
date: "11/30/2019"
output:
  word_document: default
  html_document: default
---

```{r loadlib, echo=T, results='hide', message=F, warning=F}
remove(list = ls())
library(data.table)
library(sandwich)
library(tidyverse)
library(lmtest)
library(ggplot2)
library(knitr)
library(psych)
library(dplyr)
library(tidyr)
library(scales)
library(RColorBrewer)
library(reshape)
library(clusterSim)
library(wordcloud)
```


```{r}
inp=fread(file="~/Downloads/VTINP16_upd.TXT")
revcode=fread(file="~/Downloads/VTREVCODE16.TXT")
rev=revcode[,c(5,7,10)]
DRG=fread(file="~/Downloads/DRG.csv")
PCCR=fread(file="~/Downloads/PCCR.csv")
inp_new=fread(file="~/Downloads/VTINP16_upd.TXT",
           col.names=c('Uniq','DRG'),
           select = c('UNIQ','DRG'))
inp_new=inp_new[DRG>=20&DRG<=977]

```


```{r}
inp_rev=merge(inp_new,rev,by="Uniq",all.x = FALSE)
inp_rev=inp_rev[REVCHRGS>100|REVCHRGS==100]
charge_ad=inp_rev[,.(charge=sum(REVCHRGS,na.rm=TRUE)),keyby =.(Uniq,DRG,PCCR)]
charge_ad=charge_ad[!is.na(PCCR)]
charge_ad=merge(charge_ad,DRG,by="DRG",all.x=TRUE)
charge_ad=merge(charge_ad,PCCR,by="PCCR",all.x=TRUE)
charge_ad=charge_ad[,-c(1,2)]
colnames(charge_ad) <- c("Uniq", "charge","DRG","PCCR")
```


```{r}
total_charge=charge_ad[,.(num_ad=.N,total=sum(charge,na.rm=TRUE)),keyby =.(DRG,PCCR)]
avg_charge=total_charge[,.(average=total/num_ad),keyby =.(DRG,PCCR)]
```

```{r}
table=cast(avg_charge,DRG~PCCR)
table=table[,-56]
table=table[-688,]
rownames(table)=table$DRG
table_new=table[,-1]
```

```{r}
table_new$PCCR_OR_and_Anesth_Costs=table_new[,"Operating Room"]+table_new[,"Anesthesiology"]
table_new[is.na(table_new)]=0
#table_new
#write.csv(table_new, file="~/Downloads/table_new.csv")
```

```{r}
cluster_data=table_new[,55]
cost=as.data.frame(cluster_data)
rownames(cost)=table$DRG
check=cost
check$name=rownames(cost)
check=as.data.table(check)
```

```{r}
# Calinski-Harabaz f-stat
set.seed(123456)
for (i in 2:5) {
  result=kmeans(cost,i)
  print(index.G1(cost,result$cluster,centrotypes="centroids"))
}
```


```{r}
set.seed(1234)
result=kmeans(cost,3)
# mean cost of the clusters
result[2]
```

```{r}
# DRG under each clusters
DRG_cluster=as.data.frame(result[1])
#write.csv(DRG_cluster, file="~/Downloads/DRG_cluster.csv")
cost_2=cost
cost_2$DRG=table$DRG
DRG_cluster_2=DRG_cluster
DRG_cluster_2$DRG=table$DRG
plot_data=merge(DRG_cluster_2,cost_2,by= "DRG",all=FALSE)
colnames(plot_data)=c("DRG","group","cost")

data=plot_data
data$group=as.character(data$group)

ggplot(data, aes(DRG, cost, color = group)) + geom_point()+
  labs(x = "DRG", y = "Cost($)", color = "Group\n")+ scale_color_manual(labels = c("low cost", "medium cost","high cost"), values = c("#008080", "#ffcc5c","#d9534f"))+
  theme(axis.text.x=element_blank(),
        axis.ticks.x=element_blank())
```


```{r}
colnames(data) <- c("Name", "group","cost")
low=data[data$group=="1",]
medium=data[data$group=="2",]
high=data[data$group=="3",]
low=merge(low,DRG,by="Name")
medium=merge(medium,DRG,by="Name")
high=merge(high,DRG,by="Name")
```

# analysis of low cost

inp features
- hospital share HHI: 0.1885219;hospital num HHI 0.1822806
top hospital is University of Vermont Medical Center (as of 2014)
— admission type: Emergency is the most common
- average pdays: 4.274434


```{r}
inp_data=inp[,c(1,2,54,76)]

low_inp=merge(inp_data,low,by="DRG",all=FALSE)
low_inp=as.data.table(low_inp)
low_inp=low_inp[cost!=0]

hospital_share=low_inp[,.(cost=sum(cost)),keyby =.(hnum2)]
hospital_share$share=hospital_share$cost/(sum(hospital_share$cost))
hospital_share=hospital_share[order(-share)]
hospital_share$share_2=hospital_share$share*hospital_share$share
low_hhi_share=sum(hospital_share$share_2)

hospital_num=low_inp[,.(number=.N),keyby =.(hnum2)]
hospital_num$share=hospital_num$number/(sum(hospital_num$number))
hospital_num=hospital_num[order(-share)]
hospital_num$share_2=hospital_num$share*hospital_num$share
low_hhi_num=sum(hospital_num$share_2)


adtype=low_inp[,.(number=.N),keyby =.(ATYPE)]
adtype=adtype[order(-number)]

pdays=low_inp[,.(number=.N),keyby =.(pdays)]
pdays=pdays[order(-number)]
sum(pdays$number)
sum(pdays$pdays*pdays$number)/37714
```

revcode features

- Top 5 expenditure of service:
Room & Board (Semi-Private 2 beds)
Laboratory - Clinical Diagnostic
Emergency Room
Pharmacy
Psychiatric

- Top 5 common service:
Pharmacy
Drugs Require Specific ID: Drugs requiring detail coding
Pharmacy: Other
Drugs Require Specific ID: Self admin drugs (insulin admin in emergency-diabetes coma)
Laboratory - Clinical Diagnostic

```{r}
rev_2=revcode[,c(5,6,7,8,10)]
inp_rev_2=merge(inp_new,rev_2,by="Uniq",all.x = FALSE)
inp_rev_2=inp_rev_2[,c(2:5)]
low_rev=merge(inp_rev_2,low,by="DRG",all=FALSE)
low_rev=low_rev[cost!=0]

REVCODE_share=low_rev[,.(total=sum(REVCHRGS)),keyby =.(REVCODE)]
REVCODE_share=REVCODE_share[order(-total)]

REVCODE_num=low_rev[,.(number=sum(REVUNITS)),keyby =.(REVCODE)]
REVCODE_num=REVCODE_num[order(-number)]

```




# analysis of medium cost

inp features
- hospital share HHI:  0.2590445;hospital num HHI 0.253887
top hospital is University of Vermont Medical Center (as of 2014)
— admission type: Elective is the most common
- average pdays: 4.673648



```{r}
inp_data=inp[,c(1,2,54,76)]

medium_inp=merge(inp_data,medium,by="DRG",all=FALSE)
medium_inp=as.data.table(medium_inp)
medium_inp=medium_inp[cost!=0]

hospital_share=medium_inp[,.(cost=sum(cost)),keyby =.(hnum2)]
hospital_share$share=hospital_share$cost/(sum(hospital_share$cost))
hospital_share=hospital_share[order(-share)]
hospital_share$share_2=hospital_share$share*hospital_share$share
medium_hhi_share=sum(hospital_share$share_2)

hospital_num=medium_inp[,.(number=.N),keyby =.(hnum2)]
hospital_num$share=hospital_num$number/(sum(hospital_num$number))
hospital_num=hospital_num[order(-share)]
hospital_num$share_2=hospital_num$share*hospital_num$share
medium_hhi_num=sum(hospital_num$share_2)

adtype=medium_inp[,.(number=.N),keyby =.(ATYPE)]
adtype=adtype[order(-number)]

pdays=medium_inp[,.(number=.N),keyby =.(pdays)]
pdays=pdays[order(-number)]
sum(pdays$number)
sum(pdays$pdays*pdays$number)/10504

```

revcode features

- Top 5 expenditure of service:
Operating Room Services
Medical/Surgical Supplies: Other implants
Room & Board (Semi-Private 2 beds)
Pharmacy
Anesthesia

- Top 5 common service:
Pharmacy
Anesthesia
Operating Room Services
Drugs Require Specific ID: Drugs requiring detail coding
Drugs Require Specific ID: Self admin drugs (insulin admin in emergency-diabetes coma)

```{r}
rev_2=revcode[,c(5,6,7,8,10)]
inp_rev_2=merge(inp_new,rev_2,by="Uniq",all.x = FALSE)
inp_rev_2=inp_rev_2[,c(2:5)]
medium_rev=merge(inp_rev_2,medium,by="DRG",all=FALSE)
medium_rev=medium_rev[cost!=0]

REVCODE_share=medium_rev[,.(total=sum(REVCHRGS)),keyby =.(REVCODE)]
REVCODE_share=REVCODE_share[order(-total)]

REVCODE_num=medium_rev[,.(number=sum(REVUNITS)),keyby =.(REVCODE)]
REVCODE_num=REVCODE_num[order(-number)]

```


# analysis of high cost

inp features
- hospital share HHI:  0.7596885; hospital num HHI 0.7545897
top hospital is University of Vermont Medical Center (as of 2014)
— admission type: Elective is the most common
- average pdays: 9.486261


```{r}
inp_data=inp[,c(1,2,54,76)]

high_inp=merge(inp_data,high,by="DRG",all=FALSE)
high_inp=as.data.table(high_inp)
high_inp=high_inp[cost!=0]

hospital_share=high_inp[,.(cost=sum(cost)),keyby =.(hnum2)]
hospital_share$share=hospital_share$cost/(sum(hospital_share$cost))
hospital_share=hospital_share[order(-share)]
hospital_share$share_2=hospital_share$share*hospital_share$share
high_hhi_share=sum(hospital_share$share_2)

hospital_num=high_inp[,.(number=.N),keyby =.(hnum2)]
hospital_num$share=hospital_num$number/(sum(hospital_num$number))
hospital_num=hospital_num[order(-share)]
hospital_num$share_2=hospital_num$share*hospital_num$share
high_hhi_num=sum(hospital_num$share_2)

adtype=high_inp[,.(number=.N),keyby =.(ATYPE)]
adtype=adtype[order(-number)]

pdays=high_inp[,.(number=.N),keyby =.(pdays)]
pdays=pdays[order(-number)]
sum(pdays$number)
sum(pdays$pdays*pdays$number)/1201
```


revcode features

- Top 5 expenditure of service:
Operating Room Services
Room & Board (Semi-Private 2 beds)
Medical/Surgical Supplies: Other implants
Intensive care
Pharmacy

- Top 5 common service:
Pharmacy
Drugs Require Specific ID: Drugs requiring detail coding
Operating Room Services
Anesthesia
Drugs Require Specific ID: Self admin drugs (insulin admin in emergency-diabetes coma)


```{r}
rev_2=revcode[,c(5,6,7,8,10)]
inp_rev_2=merge(inp_new,rev_2,by="Uniq",all.x = FALSE)
inp_rev_2=inp_rev_2[,c(2:5)]
high_rev=merge(inp_rev_2,high,by="DRG",all=FALSE)
high_rev=high_rev[cost!=0]

REVCODE_share=high_rev[,.(total=sum(REVCHRGS)),keyby =.(REVCODE)]
REVCODE_share=REVCODE_share[order(-total)]

REVCODE_num=high_rev[,.(number=sum(REVUNITS)),keyby =.(REVCODE)]
REVCODE_num=REVCODE_num[order(-number)]

```

```{r}
drg_cluster_low=as.data.frame(low_inp$Name)
colnames(drg_cluster_low)=c("name")
drg_cluster_low$name=as.character(factor(drg_cluster_low$name))

List <- strsplit(drg_cluster_low$name, " ")
List=data.frame(Words=unlist(List))
List=as.data.table(List)
List=List[,.(number=.N),keyby=.(Words)]
List=List[order(-number)]
List=List[-c(1,2,3,5,11,12,13,14,15,16,19,20,21)]
List=List[-c(13:16)]
List=List[-c(36)]
List=List[-c(3)]

#cloud_low=List %>%with(wordcloud(Words, number, max.words = 80,colors=brewer.pal(8, "Dark2")))
```

```{r}
drg_cluster_medium=as.data.frame(medium_inp$Name)
colnames(drg_cluster_medium)=c("name")
drg_cluster_medium$name=as.character(factor(drg_cluster_medium$name))

List <- strsplit(drg_cluster_medium$name, " ")
List=data.frame(Words=unlist(List))
List=as.data.table(List)
List=List[,.(number=.N),keyby=.(Words)]
List=List[order(-number)]

List=List[-c(11,15)]


#cloud_low=List %>%with(wordcloud(Words, number, max.words = 80,colors=brewer.pal(8, "Dark2")))
```

```{r}
inp_data=inp[,c(1,2,4,6,54,76)]
low_gender=merge(inp_data,low,by="DRG",all=FALSE)[,5]
low_gender=low_gender[,.(number=.N),keyby=.(sex)]
low_gender=low_gender[-1,]
17616+23540	
low_gender=low_gender[,.(percentage=number/41156),keyby=.(sex)]
```

```{r}
inp_data=inp[,c(1,2,4,6,54,76)]
medium_gender=merge(inp_data,medium,by="DRG",all=FALSE)[,5]
medium_gender=medium_gender[,.(number=.N),keyby=.(sex)]
medium_gender
4867+5637
medium_gender=medium_gender[,.(percentage=number/10504),keyby=.(sex)]
```

```{r}
inp_data=inp[,c(1,2,4,6,54,76)]
high_gender=merge(inp_data,high,by="DRG",all=FALSE)[,5]
high_gender=high_gender[,.(number=.N),keyby=.(sex)]
753+448	
high_gender=high_gender[,.(percentage=number/1201),keyby=.(sex)]
```
48.87745
```{r}
age=fread(file="~/Downloads/age.csv",col.names=c('intage','median'),select = c('AGEGRP','median'))
inp_data=inp[,c(1,2,4,6,54,76)]
row_number=merge(inp_data,low,by="DRG",all=FALSE)[,4]
low_age=merge(inp_data,low,by="DRG",all=FALSE)[,4]
low_age=merge(low_age,age,by="intage",all=FALSE)

low_age=low_age[,.(number=.N),keyby=.(median)]
average=sum(low_age$median*low_age$number)/nrow(row_number)
```

60.04446

```{r}
age=fread(file="~/Downloads/age.csv",col.names=c('intage','median'),select = c('AGEGRP','median'))
inp_data=inp[,c(1,2,4,6,54,76)]
row_number=merge(inp_data,medium,by="DRG",all=FALSE)[,4]
medium_age=merge(inp_data,medium,by="DRG",all=FALSE)[,4]
medium_age=merge(medium_age,age,by="intage",all=FALSE)

medium_age=medium_age[,.(number=.N),keyby=.(median)]
average=sum(medium_age$median*medium_age$number)/nrow(row_number)
```

60.81848

```{r}
age=fread(file="~/Downloads/age.csv",col.names=c('intage','median'),select = c('AGEGRP','median'))
inp_data=inp[,c(1,2,4,6,54,76)]
row_number=merge(inp_data,high,by="DRG",all=FALSE)[,4]
high_age=merge(inp_data,high,by="DRG",all=FALSE)[,4]
high_age=merge(high_age,age,by="intage",all=FALSE)

high_age=high_age[,.(number=.N),keyby=.(median)]
average=sum(high_age$median*high_age$number)/nrow(row_number)
```




