---
title: "Healthcare Analysis Assignment-2"
author: "group 3"
date: "11/12/2019"
output:
  word_document: default
  pdf_document: default
  html_document: default
---

```{r loadlib, echo=T, results='hide', message=F, warning=F}
rm(list=ls())
library(data.table)
library(sandwich)
library(tidyverse)
library(lmtest)
library(ggplot2)
library(knitr)
library(psych)
library(dplyr)
```

## Question 3

```{r}
EOC170=fread(file="~/Downloads/EOC170.csv",
           col.names=c('Contract_Number','Plan_Name','UOD'),
           select = c('Contract Number','Plan Name','EOC170-0010'))
EOC170=EOC170[UOD!="0.00"&!is.na(UOD)&UOD!="NB"&UOD!="BR"&UOD!="NQ"]
EOC170$UOD_rate=as.numeric(EOC170$UOD)/1000
```

```{r}
enrollment=fread(file="~/Downloads/CPSC_Enrollment_2019_10/CPSC_Enrollment_Info_2019_10.csv",
           col.names=c('Contract_Number','Plan_ID','State','Enrollment'),
           select = c('Contract Number','Plan ID','State','Enrollment'))
enrollment=enrollment[Enrollment!="*"&!is.na(Enrollment)]
enrollment=enrollment[str_sub(enrollment$Contract_Number,1,1)!="S"]
enrollment=enrollment[State=='FL'|State=='NC'|State=='MA'|State=='CO'|State=='OR'|State=='AR'|State=='WV'|State=='MT'|State=='VT']
enrollment=enrollment[,.(enrollment=sum(as.numeric(Enrollment))),keyby =.(Contract_Number,Plan_ID,State)]
```


```{r}
contract_sub_org=fread(file="~/Downloads/Monthly_Report_By_Plan_2019_10/Monthly_Report_By_Plan_2019_10.csv",
                 col.names=c('Contract_Number','Plan_ID','Organization Marketing Name'),
                 select = c('Contract Number','Plan ID','Organization Marketing Name'))
```

```{r}
MajorInsuranceOrgs=fread(file="~/Downloads/MajorInsuranceOrgs.csv",
                   col.names=c('Organization Marketing Name','Parent_Organization'),
                   select = c('Organization Marketing Name','MajorInsuranceOrgName'))
```

```{r}
contract_parent_org=merge(contract_sub_org,MajorInsuranceOrgs,by=c("Organization Marketing Name"),all.x=TRUE)
```



```{r}
enrollment_contract=merge(enrollment,contract_parent_org,by=c("Contract_Number","Plan_ID"),all=FALSE)
enrollment_contract=enrollment_contract[Parent_Organization!=is.na(Parent_Organization),]
enrollment_contract=enrollment_contract[,.(State,Parent_Organization,Contract_Number,Plan_ID,enrollment)]
enrollment_contract=enrollment_contract[,.(enrollment=sum(enrollment)),keyby =.(Contract_Number,Parent_Organization,State)]
enrollment_contract=enrollment_contract[order(State,Contract_Number)]
```

```{r}
plan_UOD=merge(enrollment_contract,EOC170,by=c("Contract_Number"),all=FALSE)
select_cols=c('State','Parent_Organization','Contract_Number','enrollment','UOD_rate')
plan_UOD=plan_UOD[,..select_cols]
plan_UOD=plan_UOD[order(State,Contract_Number)]
```

```{r}
enrollment_new=fread(file="~/Downloads/CPSC_Enrollment_2019_10/CPSC_Enrollment_Info_2019_10.csv",
           col.names=c('Contract_Number','Plan_ID','State'),
           select = c('Contract Number','Plan ID','State'))
enrollment_new=enrollment_new[str_sub(enrollment_new$Contract_Number,1,1)!="S"]
enrollment_new=enrollment_new[State=='FL'|State=='NC'|State=='MA'|State=='CO'|State=='OR'|State=='AR'|State=='WV'|State=='MT'|State=='VT']
contract_parent=merge(enrollment_new,contract_parent_org,by=c("Contract_Number","Plan_ID"),all=FALSE)
contract_parent_UOD=merge(contract_parent,EOC170,by=c("Contract_Number"),all=FALSE)
```


```{r}
share=fread(file="~/Downloads/share.csv",
           col.names=c('State','Parent_Organization','share'),
           select = c('State','MajorInsuranceOrgName','share'))
share=share[order(State)]
```

TOP 10 companies' UOD condition in AR

```{r}
AR_TOP10=share[State=='AR']
AR_TOP10=AR_TOP10[order(-share)]
AR_TOP10=AR_TOP10[1:10]
AR_UOD=merge(AR_TOP10,plan_UOD,by=c("State","Parent_Organization"),all=FALSE)
AR_UOD_1=merge(AR_TOP10,contract_parent_UOD,by=c("State","Parent_Organization"),all=FALSE)
AR_UOD_1=AR_UOD_1[,.(UOD_rate=unique(UOD_rate)),keyby =.(Contract_Number,Parent_Organization,State)]
```

TOP 10 companies' UOD condition in CO

```{r}
CO_TOP10=share[State=='CO']
CO_TOP10=CO_TOP10[order(-share)]
CO_TOP10=CO_TOP10[1:10]
CO_UOD=merge(CO_TOP10,plan_UOD,by=c("State","Parent_Organization"),all=FALSE)
CO_UOD_1=merge(CO_TOP10,contract_parent_UOD,by=c("State","Parent_Organization"),all=FALSE)
CO_UOD_1=CO_UOD_1[,.(UOD_rate=unique(UOD_rate)),keyby =.(Contract_Number,Parent_Organization,State)]
```

TOP 10 companies' UOD condition in FL

```{r}
FL_TOP10=share[State=='FL']
FL_TOP10=FL_TOP10[order(-share)]
FL_TOP10=FL_TOP10[1:10]
FL_UOD=merge(FL_TOP10,plan_UOD,by=c("State","Parent_Organization"),all=FALSE)
FL_UOD_1=merge(FL_TOP10,contract_parent_UOD,by=c("State","Parent_Organization"),all=FALSE)
FL_UOD_1=FL_UOD_1[,.(UOD_rate=unique(UOD_rate)),keyby =.(Contract_Number,Parent_Organization,State)]
```

TOP 10 companies' UOD condition in MA

```{r}
MA_TOP10=share[State=='MA']
MA_TOP10=MA_TOP10[order(-share)]
MA_TOP10=MA_TOP10[1:10]
MA_UOD=merge(MA_TOP10,plan_UOD,by=c("State","Parent_Organization"),all=FALSE)
MA_UOD_1=merge(MA_TOP10,contract_parent_UOD,by=c("State","Parent_Organization"),all=FALSE)
MA_UOD_1=MA_UOD_1[,.(UOD_rate=unique(UOD_rate)),keyby =.(Contract_Number,Parent_Organization,State)]
```

TOP 10 companies' UOD condition in MT

```{r}
MT_TOP10=share[State=='MT']
MT_TOP10=MT_TOP10[order(-share)]
MT_TOP10=MT_TOP10[1:10]
MT_UOD=merge(MT_TOP10,plan_UOD,by=c("State","Parent_Organization"),all=FALSE)
MT_UOD_1=merge(MT_TOP10,contract_parent_UOD,by=c("State","Parent_Organization"),all=FALSE)
MT_UOD_1=MT_UOD_1[,.(UOD_rate=unique(UOD_rate)),keyby =.(Contract_Number,Parent_Organization,State)]
```

TOP 10 companies' UOD condition in NC

```{r}
NC_TOP10=share[State=='NC']
NC_TOP10=NC_TOP10[order(-share)]
NC_TOP10=NC_TOP10[1:10]
NC_UOD=merge(NC_TOP10,plan_UOD,by=c("State","Parent_Organization"),all=FALSE)
NC_UOD_1=merge(NC_TOP10,contract_parent_UOD,by=c("State","Parent_Organization"),all=FALSE)
NC_UOD_1=NC_UOD_1[,.(UOD_rate=unique(UOD_rate)),keyby =.(Contract_Number,Parent_Organization,State)]
```

TOP 10 companies' UOD condition in OR

```{r}
OR_TOP10=share[State=='OR']
OR_TOP10=OR_TOP10[order(-share)]
OR_TOP10=OR_TOP10[1:10]
OR_UOD=merge(OR_TOP10,plan_UOD,by=c("State","Parent_Organization"),all=FALSE)
OR_UOD_1=merge(OR_TOP10,contract_parent_UOD,by=c("State","Parent_Organization"),all=FALSE)
OR_UOD_1=OR_UOD_1[,.(UOD_rate=unique(UOD_rate)),keyby =.(Contract_Number,Parent_Organization,State)]
```

TOP 10 companies' UOD condition in VT

```{r}
VT_TOP10=share[State=='VT']
VT_TOP10=VT_TOP10[order(-share)]
VT_TOP10=VT_TOP10[1:10]
VT_UOD=merge(VT_TOP10,plan_UOD,by=c("State","Parent_Organization"),all=FALSE)
VT_UOD_1=merge(VT_TOP10,contract_parent_UOD,by=c("State","Parent_Organization"),all=FALSE)
VT_UOD_1=VT_UOD_1[,.(UOD_rate=unique(UOD_rate)),keyby =.(Contract_Number,Parent_Organization,State)]
```

TOP 10 companies' UOD condition in WV

```{r}
WV_TOP10=share[State=='WV']
WV_TOP10=WV_TOP10[order(-share)]
WV_TOP10=WV_TOP10[1:10]
WV_UOD=merge(WV_TOP10,plan_UOD,by=c("State","Parent_Organization"),all=FALSE)
WV_UOD_1=merge(WV_TOP10,contract_parent_UOD,by=c("State","Parent_Organization"),all=FALSE)
WV_UOD_1=WV_UOD_1[,.(UOD_rate=unique(UOD_rate)),keyby=.(Contract_Number,Parent_Organization,State)]
```

Summary of UOD condition of top 10 companies in all 9 states:

```{r}
UOD_top10_state=rbind(AR_UOD_1,CO_UOD_1,FL_UOD_1,MA_UOD_1,MT_UOD_1,NC_UOD_1,OR_UOD_1,VT_UOD_1,WV_UOD_1)
UOD_top10_state=UOD_top10_state[order(State,Parent_Organization,Contract_Number)]
```


weight average for each state's top 10 companies:

TOP 10 companies' UOD weight average in AR

```{r}
AR_UOD_org=AR_UOD[,.(UOD_population=enrollment*UOD_rate),keyby=.(Contract_Number,Parent_Organization,State)]
AR_UOD_org=AR_UOD_org[,.(total_UOD_population=sum(UOD_population)),keyby=.(Parent_Organization,State)]
AR_enrollment_org=AR_UOD[,.(total_enrollment=sum(enrollment)),keyby=.(Parent_Organization,State)]
AR_weight_average=merge(AR_UOD_org,AR_enrollment_org,by='Parent_Organization',all.x=FALSE)
AR_weight_average=AR_weight_average[,.(weight_average=total_UOD_population/total_enrollment),keyby=.(Parent_Organization,State.x)]
AR_weight_average=AR_weight_average[ORDER(-weight_average)]
```

TOP 10 companies' UOD weight average in CO

```{r}
CO_UOD_org=CO_UOD[,.(UOD_population=enrollment*UOD_rate),keyby=.(Contract_Number,Parent_Organization,State)]
CO_UOD_org=CO_UOD_org[,.(total_UOD_population=sum(UOD_population)),keyby=.(Parent_Organization,State)]
CO_enrollment_org=CO_UOD[,.(total_enrollment=sum(enrollment)),keyby=.(Parent_Organization,State)]
CO_weight_average=merge(CO_UOD_org,CO_enrollment_org,by='Parent_Organization',all.x=FALSE)
CO_weight_average=CO_weight_average[,.(weight_average=total_UOD_population/total_enrollment),keyby=.(Parent_Organization,State.x)]
CO_weight_average=CO_weight_average[ORDER(-weight_average)]
```

TOP 10 companies' UOD weight average in FL

```{r}
FL_UOD_org=FL_UOD[,.(UOD_population=enrollment*UOD_rate),keyby=.(Contract_Number,Parent_Organization,State)]
FL_UOD_org=FL_UOD_org[,.(total_UOD_population=sum(UOD_population)),keyby=.(Parent_Organization,State)]
FL_enrollment_org=FL_UOD[,.(total_enrollment=sum(enrollment)),keyby=.(Parent_Organization,State)]
FL_weight_average=merge(FL_UOD_org,FL_enrollment_org,by='Parent_Organization',all.x=FALSE)
FL_weight_average=FL_weight_average[,.(weight_average=total_UOD_population/total_enrollment),keyby=.(Parent_Organization,State.x)]
FL_weight_average=FL_weight_average[ORDER(-weight_average)]
```

TOP 10 companies' UOD weight average in MA

```{r}
MA_UOD_org=MA_UOD[,.(UOD_population=enrollment*UOD_rate),keyby=.(Contract_Number,Parent_Organization,State)]
MA_UOD_org=MA_UOD_org[,.(total_UOD_population=sum(UOD_population)),keyby=.(Parent_Organization,State)]
MA_enrollment_org=MA_UOD[,.(total_enrollment=sum(enrollment)),keyby=.(Parent_Organization,State)]
MA_weight_average=merge(MA_UOD_org,MA_enrollment_org,by='Parent_Organization',all.x=FALSE)
MA_weight_average=MA_weight_average[,.(weight_average=total_UOD_population/total_enrollment),keyby=.(Parent_Organization,State.x)]
MA_weight_average=MA_weight_average[ORDER(-weight_average)]
```

TOP 10 companies' UOD weight average in MT

```{r}
MT_UOD_org=MT_UOD[,.(UOD_population=enrollment*UOD_rate),keyby=.(Contract_Number,Parent_Organization,State)]
MT_UOD_org=MT_UOD_org[,.(total_UOD_population=sum(UOD_population)),keyby=.(Parent_Organization,State)]
MT_enrollment_org=MT_UOD[,.(total_enrollment=sum(enrollment)),keyby=.(Parent_Organization,State)]
MT_weight_average=merge(MT_UOD_org,MT_enrollment_org,by='Parent_Organization',all.x=FALSE)
MT_weight_average=MT_weight_average[,.(weight_average=total_UOD_population/total_enrollment),keyby=.(Parent_Organization,State.x)]
MT_weight_average=MT_weight_average[ORDER(-weight_average)]
```

TOP 10 companies' UOD weight average in NC

```{r}
NC_UOD_org=NC_UOD[,.(UOD_population=enrollment*UOD_rate),keyby=.(Contract_Number,Parent_Organization,State)]
NC_UOD_org=NC_UOD_org[,.(total_UOD_population=sum(UOD_population)),keyby=.(Parent_Organization,State)]
NC_enrollment_org=NC_UOD[,.(total_enrollment=sum(enrollment)),keyby=.(Parent_Organization,State)]
NC_weight_average=merge(NC_UOD_org,NC_enrollment_org,by='Parent_Organization',all.x=FALSE)
NC_weight_average=NC_weight_average[,.(weight_average=total_UOD_population/total_enrollment),keyby=.(Parent_Organization,State.x)]
NC_weight_average=NC_weight_average[ORDER(-weight_average)]
```

TOP 10 companies' UOD weight average in OR

```{r}
OR_UOD_org=OR_UOD[,.(UOD_population=enrollment*UOD_rate),keyby=.(Contract_Number,Parent_Organization,State)]
OR_UOD_org=OR_UOD_org[,.(total_UOD_population=sum(UOD_population)),keyby=.(Parent_Organization,State)]
OR_enrollment_org=OR_UOD[,.(total_enrollment=sum(enrollment)),keyby=.(Parent_Organization,State)]
OR_weight_average=merge(OR_UOD_org,OR_enrollment_org,by='Parent_Organization',all.x=FALSE)
OR_weight_average=OR_weight_average[,.(weight_average=total_UOD_population/total_enrollment),keyby=.(Parent_Organization,State.x)]
OR_weight_average=OR_weight_average[ORDER(-weight_average)]
```

TOP 10 companies' UOD weight average in VT

```{r}
VT_UOD_org=VT_UOD[,.(UOD_population=enrollment*UOD_rate),keyby=.(Contract_Number,Parent_Organization,State)]
VT_UOD_org=VT_UOD_org[,.(total_UOD_population=sum(UOD_population)),keyby=.(Parent_Organization,State)]
VT_enrollment_org=VT_UOD[,.(total_enrollment=sum(enrollment)),keyby=.(Parent_Organization,State)]
VT_weight_average=merge(VT_UOD_org,VT_enrollment_org,by='Parent_Organization',all.x=FALSE)
VT_weight_average=VT_weight_average[,.(weight_average=total_UOD_population/total_enrollment),keyby=.(Parent_Organization,State.x)]
VT_weight_average=VT_weight_average[ORDER(-weight_average)]
```

TOP 10 companies' UOD weight average in WV

```{r}
WV_UOD_org=WV_UOD[,.(UOD_population=enrollment*UOD_rate),keyby=.(Contract_Number,Parent_Organization,State)]
WV_UOD_org=WV_UOD_org[,.(total_UOD_population=sum(UOD_population)),keyby=.(Parent_Organization,State)]
WV_enrollment_org=WV_UOD[,.(total_enrollment=sum(enrollment)),keyby=.(Parent_Organization,State)]
WV_weight_average=merge(WV_UOD_org,WV_enrollment_org,by='Parent_Organization',all.x=FALSE)
WV_weight_average=WV_weight_average[,.(weight_average=total_UOD_population/total_enrollment),keyby=.(Parent_Organization,State.x)]
WV_weight_average=WV_weight_average[ORDER(-weight_average)]
```

Summary of UOD weight average of top 10 companies in all 9 states:

```{r}
weight_average_top10_state=rbind(AR_weight_average,CO_weight_average,FL_weight_average,MA_weight_average,MT_weight_average,NC_weight_average,OR_weight_average,VT_weight_average,WV_weight_average)
```

save the results

```{r}
write.csv(UOD_top10_state, file="~/Downloads/UOD_top10_state.csv")
write.csv(weight_average_top10_state, file="~/Downloads/weight_average_top10_state.csv")
```



























